### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
Regmachine: some more love

\begin{definition}
  We say that a set $\eventSet$ together with strict partial order $\identOrd$
  form an identifier set if:
  \begin{itemize}
    \item there exists a distinguished initial identifier $e_0 \in \eventSet$;
    \item there exists a function $\fresh : \eventSet \fun \eventSet$ which 
      generates a new fresh identifier, \sth
      $$ \forall e \in \eventSet \ldotp e \identOrd \fresh(e) $$
  \end{itemize}
\end{definition}

@@

The first component $\eventSeq$ is a sequence of events 
$e_1 \identOrdDual \dots \identOrdDual e_n$
in the order reverse to the the one 
in which events are added to the structure. 
The second component is labelling function $\lLAB : \eventSet \fun \Lab$, 
assigning a label to each event.

>>>>

\begin{definition}
  We say that a set $\eventSet$ together with strict partial order $\identOrd$
  form an \emph{identifier set} if:
  \begin{itemize}
    \item there exists a distinguished initial identifier $e_0 \in \eventSet$;
    \item there exists a function $\fresh : \eventSet \fun \eventSet$ which 
      generates a new fresh identifier, \sth
      $$ \forall e \in \eventSet \ldotp e \identOrd \fresh(e) $$
  \end{itemize}
\end{definition}

@@

The first component $\eventSeq$ is a sequence of events 
$e_1 \identOrdDual \dots \identOrdDual e_n$
in reverse order w.r.t the order 
in which events get added to the structure. 
The second component is a labelling function $\lLAB : \eventSet \fun \Lab$, 
assigning a label to each event.
